Case for Support

### 2021-11-16 application/caseForSupport.tex

\documentclass[a4paper,11point]{article}
\usepackage[margin=2cm]{geometry}
%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage{microtype}      % fine pdf font control

@@

\usepackage{wrapfig}

@@

\section{Potential for economic and societal impact}
\textbf{Understanding the brain and behaviour.} Systems neuroscientists aim to uncover how adaptive behaviour arises
from computation in neural circuits in different brain regions. Extending the Bonsai ecosystem will facilitate new types of experiment that causally connect neural circuits with elemental behavioural processes. Long-term, this research will help identify the missing links between circuit dysfunction and behavioural deficits in neurological or mental health disorders, and will pave the way for the development of new neural circuit biomarkers and therapies. The Bonsai ecosystem will also enable the experimental testing of emerging theories of brain function and learning, and thus contribute to the neuro-inspired machine learning algorithms that fuel intelligent technologies, increasingly important in our society.
The enhanced Bonsai platform will also support purely behavioural experiments, in which the animals' posture, body parts or location are tracked in real-time, allowing investigation of environmental impacts and captivit the impact of the envuronmental variables in behaviour but also enhace monitoring of intaractive experimental designs animals or other

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[margin=2cm]{geometry}
%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage{microtype}      % fine pdf font control

@@

\usepackage{float}
\usepackage{wrapfig}

@@

\section{Potential for economic and societal impact}
\textbf{Understanding the brain and behaviour.} Systems neuroscientists aim to uncover how adaptive behaviour arises
from computation in neural circuits in different brain regions. Extending the Bonsai ecosystem will facilitate new types of experiment that causally connect neural circuits with elemental behavioural processes. Long-term, this research will help identify the missing links between circuit dysfunction and behavioural deficits in neurological or mental health disorders, and will pave the way for the development of new neural circuit biomarkers and therapies. The Bonsai ecosystem will also enable the experimental testing of emerging theories of brain function and learning, and thus contribute to the neuro-inspired machine learning algorithms that fuel intelligent technologies, increasingly important in our society.
The enhanced Bonsai platform will also support purely behavioural experiments, in which the animals' posture, body parts or location are tracked in real-time, allowing investigation of environmental variables or captivity on their behaviour, especially important for assessment of animal welfare.
